Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-10 WSSSPE3/report/wg_main_metrics.tex
fixing a build problem

\item
2015 NSF SI2 PI Workshop Breakout Session on Framing Success Metrics\footnote{\url{https://docs.google.com/document/d/10yj7MYEjvrg__t522XR41ogASYMp647-l-BpFTsqEV4/edit#heading=h.5lah0hp73q99}}

@@

\item
NSF Workshop on Software and Data Citation Breakout Group on Useful Metrics\footnote{\url{https://docs.google.com/presentation/d/1PPLVL6uoOmisqnHTlwhsVKJBTFFK1IVzvr8FdEEIvAE/edit#slide=id.g5e66ec9f2_027
}}

>>>>

\item
2015 NSF SI2 PI Workshop Breakout Session on Framing Success Metrics\footnote{\url{https://docs.google.com/document/d/10yj7MYEjvrg__t522XR41ogASYMp647-l-BpFTsqEV4/}}

@@

\item
NSF Workshop on Software and Data Citation Breakout Group on Useful Metrics\footnote{\url{https://docs.google.com/presentation/d/1PPLVL6uoOmisqnHTlwhsVKJBTFFK1IVzvr8FdEEIvAE/}}
